---
title: "AIG Portfolio"
author: "Keoshia Grigsby"
date: "March 9, 2022"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

## History

In 1919, Cornelius Vander Starr stepped off a steamship in Shanghai determined to make his mark in the world. Working from a two-room office, he established American Asiatic Underwriters, an insurance agency to which we trace our roots. Starr believed in making the world a better place and with other early company pioneers, his organization grew across the world. Today, AIG is a global insurance company with operations in more than 80 countries and jurisdictions. In 2005 Martin J. Sullivan is appointed AIG President and CEO. In 2008 AIG Chairman Robert Willumstad becomes CEO. After the financial crisis hits the U.S., the government provides support to AIG, and Edward M. Liddy becomes AIG Chairman and CEO. In 2009 Robert H. Benmosche is named AIG President and CEO. In 2014 Peter D. Hancock is named AIG President and CEO.  In May 2017 Brian Duperreault is named AIG President & CEO. In August 2020 Peter Zaffino appointed President of AIG. March 2021 he took on the additional role of Chief Executive Officer and as of January 2022 became Chairman of the Board of Directors

## Mission/objective. 
The AIG mission statement is to provide power generation and procurement solutions at a price the competitors cannot match without sacrificing high standards of service, and our clients agree that we deliver on that statement.

## Current Performance
AIG believes a commitment to sustainability helps future-proof communities by addressing societal and environmental factors, while enabling economic progress. Building on our expertise and capabilities in managing risks of many kinds, we can facilitate, design and drive innovative solutions to help clients and partners adapt to our changing world. Our four sustainability priorities align with our core business strategy and include community resilience, financial security, sustainable investing and sustainable operations. 
AIG Life & Retirement consists of four operating segments: Individual Retirement, Group Retirement, Life Insurance and Institutional Markets. It includes the following major U.S. life insurance companies: American General Life Insurance Company; The Variable Annuity Life Insurance Company; and The United States Life Insurance Company in the City of New York.






```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
#### Quarterly Sales 
#install.packages("xml2")
#install.packages("rvest")
#install.packages("tidyverse")
#install.packages("dplyr")
library(tidyverse)
library(dplyr)
library(xml2)
library(rvest)
library(lubridate)


## Sales 
AIG_stock <- read_csv("AIG.csv")
url <- "https://www.macrotrends.net/stocks/charts/AIG/american/revenue"
page <- read_html(url) #Creates an html document from URL
table <- html_table(page, fill = TRUE)#Parses tables into data frames

## Sales 

## Sales 
q_revenue_aig <- data.frame(table[2])
q_revenue_aig <- q_revenue_aig %>% rename("Date" = "American.Quarterly.Revenue.Millions.of.US...","Quarterly.Revenue" = "American.Quarterly.Revenue.Millions.of.US....1")

q_revenue_aig$Quarterly.Revenue <- as.numeric(gsub("[\\$,]", "", q_revenue_aig$Quarterly.Revenue))
q_revenue_aig$Date <- as.Date(q_revenue_aig$Date)
write_csv2(q_revenue_aig, "q_revenue_aig.csv")

pandemic_date <- AIG_stock[710, ]
Duperreault_date <- AIG_stock[35, ]
Zaffino_pres_date <- AIG_stock[860, ]
Zaffino_ceo_date <- AIG_stock[1000, ]


ylim = c(min(q_revenue_aig$Quarterly.Revenue), max(q_revenue_aig$Quarterly.Revenue))
plot(q_revenue_aig$Date, q_revenue_aig$Quarterly.Revenue, type='o', ylim=ylim, col="blue", xlab='Date', ylab='Revenue', lwd=2,frame.plot = TRUE)
abline(v = pandemic_date, col = "red")
abline(v = Duperreault_date, col = "red")
abline(v = Zaffino_pres_date, col = "red")
abline(v = Zaffino_ceo_date, col = "red")
title("AIG Quarterly Sales / Revenue")
#What can you tell from the sales graph? Is there a trend? Was there an extreme peak or dip? Using news fromyour company, explain the performance of your company.

```
* From the sales graph we can kinda see that the revenue for AIG since 2010 has been slowly decreasing unitl the year of the pandemic.
There is a trend with higher revenue leading to a new ceo but falling right after
there is an extreame peak or dip during 2013-2016 and again 2020-2021
I used the news of a new CEO and the pandemic, what I found was after AIG sees more revenue they typically name someone else CEO 



```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}



# net income 

url2 <- "https://www.macrotrends.net/stocks/charts/AIG/american/net-income"
page2 <- read_html(url2)
table2 <- html_table(page2, fill = TRUE)

q_net_income_aig <- data.frame(table2[2])
q_net_income_aig <- q_net_income_aig %>% rename("Date" = "American.Quarterly.Net.Income.Millions.of.US...", "Quarterly.Income" = "American.Quarterly.Net.Income.Millions.of.US....1")

q_net_income_aig$Quarterly.Income <- as.numeric(gsub("[\\$,]", "", q_net_income_aig$Quarterly.Income))
q_net_income_aig$Date <- as.Date(q_net_income_aig$Date)
write_csv(q_net_income_aig, "q_net_income_aig.csv")




ylim = c(min(q_net_income_aig$Quarterly.Income), max(q_net_income_aig$Quarterly.Income))
plot(q_net_income_aig$Date, q_net_income_aig$Quarterly.Income, type='l', ylim=ylim, col="blue", xlab='Date', ylab='Net Income', lwd=2,frame.plot = TRUE)
abline(h = 0, col = "red")
abline(v = pandemic_date, col = "red")
abline(v = Duperreault_date, col = "red")
abline(v = Zaffino_pres_date, col = "red")
abline(v = Zaffino_ceo_date, col = "red")
title("AIG Quarterly Income")

```

* From the Net Income Graph you can tell that overall the income for AIG stays between -5000 and 5000 except for 2012, 2018, and 2020
There is not a visible trend but when they hire a new CEO its usually after some time of a dip in Net Income
There was extreme peak during 2012 and 2 dips in 2018 and 2020
AIG was bailed out of debt by the us government in 2008 for 13billion. In 2013 AIG considered a lawsuit against the US government for making bailout conditions harder on their share holders than some banks. So in return the US department of treasury sold off their stocks, All of Them. 
In 2018 AIG experienced huge profit losses which lead to that dip in net income.
In 2020 AIG was struck by the effects of the COVID-19 pandemic


#### stocks 

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}


# stocks 
#download csv from yahoo
#What can you tell from graph? Is there a trend? Was there an extreme peak or dip? Using news from your company, explain the performance of your company. How did the company perform before Covid-19? How has Covid-19 impacted your company? What are some of the initiatives that they have performed during the pandemic?

AIG_stock <- read_csv("AIG.csv")
AIG_stock$Date <- as.Date(AIG_stock$Date, format='%m/%d/%y')


ylim = c(min(AIG_stock$High), max(AIG_stock$High))
plot(AIG_stock$Date, AIG_stock$High, type='l', ylim=ylim, col="blue", xlab='Date', ylab='Price ', lwd=2,frame.plot = FALSE)
title("AIG Stock Prices")
abline(v = pandemic_date, col = "red")
abline(v = Duperreault_date, col = "red")
abline(v = Zaffino_pres_date, col = "red")
abline(v = Zaffino_ceo_date, col = "red")

```

#download csv from yahoo
#What can you tell from graph? Is there a trend? Was there an extreme peak or dip? Using news from your company, explain the performance of your company. How did the company perform before Covid-19? How has Covid-19 impacted your company? What are some of the initiatives that they have performed during the pandemic?

* I can tell that I could have made 3 times my money had I invested during the pandemic. We can also see that AIG was hit hard by the pandemic based on their stock prices. The price of the stock stayed steady until 

websites for citing 

https://www.aig.com/about-us/sustainability
